### 2015-05-14 whoop.tex
Tweaks

\medskip\noindent\textbf{Concurrent Programming Model }
%
We consider a concurrent programming model where an unbounded number of threads execute a set of pre-defined \emph{thread templates}.  At any given point of execution a certain number of threads are active, each thread executing a particular template.  In the context of device drivers, a thread template corresponds to a driver entry point, and multiple instances of the same thread template may execute concurrently, just as multiple invocations of a single driver entry point may be concurrent.  Further threads may be launched at any point during execution; in the context of device drivers this corresponds to the OS invoking additional driver entry points.  For ease of presentation only, our model does not feature aggregate data types, pointers or dynamic memory allocation.  These \emph{are} handled by our implementation, and in \S\ref{sec:implementation} we discuss interesting practical issues arising from the handling of a full-blown language.

@@

The statements of each procedure in $\instrument{T}{i}$ that access shared variables and mutexes are instrumented to manipulate these sets.  This transformation is described in Figure~\ref{fig:instrumentation}, where for an expression $e$ we use $\instrument{e}{i}$ to denote $e$ after renaming with respect to $i$.  A shared variable assignment, $s = e$, is instrumented by recording in $\hasbeenwritten{i}$ that $s$ has been written to, and updating the lockset for $s$, $\lockset{s}{i}$, to eliminate any mutexes that are not currently held (i.e.\ those mutexes that are not in $\currentlockset{i}$).  A shared variable read, $x = s$ operates analogously, except for the additional $\havockeyword$ command which we discuss under \emph{Shared State Abstraction} below.  Instrumentation of mutex manipulation commands, $\mutexlock{m}$ and $\mutexunlock{m}$, involves updating the current lockset, $\currentlockset{i}$, to add and remove mutex $m$, respectively.

>>>>

\medskip\noindent\textbf{Concurrent Programming Model }
%
We consider a concurrent programming model where an unbounded number of threads execute a set of pre-defined \emph{thread templates}.  At any given point of execution a certain number of threads are active, each thread executing a particular template.  In the context of device drivers, a thread template corresponds to a driver entry point, and multiple instances of the same thread template may execute concurrently, just as multiple invocations of a single driver entry point may be concurrent.  Further threads may start executing at any point during execution; in the context of device drivers this corresponds to the OS invoking additional driver entry points.\footnote{We do \emph{not} consider the case where one thread spawns another thread, which does not occur in the context of drivers; rather we aim to capture the scenario where additional threads are launched by the environment.}  For ease of presentation only, our model does not feature aggregate data types, pointers or dynamic memory allocation.  These \emph{are} handled by our implementation, and in \S\ref{sec:implementation} we discuss interesting practical issues arising from the handling of a full-blown language.

@@

The statements of each procedure in $\instrument{T}{i}$ that access shared variables and mutexes are instrumented to manipulate these sets.  This transformation is described in Figure~\ref{fig:instrumentation}.  A shared variable assignment, $s = e$, is instrumented by recording in $\hasbeenwritten{i}$ that $s$ has been written to, and updating the lockset for $s$, $\lockset{s}{i}$, to eliminate any mutexes that are not currently held (i.e.\ those mutexes that are not in $\currentlockset{i}$).  A shared variable read, $x = s$ operates analogously, except for the additional $\havockeyword$ command which we discuss under \emph{Shared State Abstraction} below.  Instrumentation of mutex manipulation commands, $\mutexlock{m}$ and $\mutexunlock{m}$, involves updating the current lockset, $\currentlockset{i}$, to add and remove mutex $m$, respectively.
